Not `Won't you be my neighbor?' \\ But `Should you be my neighbor?'

### 2015-03-09 paper_skeleton.tex
ive changed how im calculating h2 and corr lengths and i think it all makes much more sense now... now i just have to write it up

To rotate into the space orthogonal to the consensus vector, we can define a matrix $Q\in\R^{N-1}\times\R^N$ such that each row of $Q$ is orthogonal to $\vec{1}$ and the rows are pairwise orthogonal. Young et al. show in \cite{Young:2010fk} show that this equivalent to finding $Q$ such that $Q\vec{1}=\vec{0}$, $QQ^T=I_{N-1}$, and $Q^TQ+I_N-\frac{1}{N}\vec{1}_N\vec{1}_N^T$. If we then define $y=Qx$, $y$ is the component of $x$ orthogonal to the consensus vector. It follows that the dynamics of $y$ follow
\begin{align*}
\dot{y}&=Q\dot{x}+Q\xi
\\&=QLx+Q\xi
\\&=QL\big(x-\frac{1}{N}\sum_kx_k\vec{1}\big)+Q\xi \text{ since } L\vec{1}=0
\\&=QLQ^TQx+Q\xi
\\&=QLQ^Ty+Q\xi
\\&=\tilde{L}y+Q\xi.
\end{align*}
Now, $y=\vec{0}$ \emph{is} globally asymptotically stable, so analyzing its variance at steady state is a well-defined problem. Young et al. show in \cite{Young:2010fk} and we show below in Claim \ref{lyapeq_derivation} that if $\Sigma=\lim_{t\to\infty}E[y(t)y^T(t)]$, then $\Sigma$ satisfies $\tilde{L}\Sigma+\Sigma \tilde{L}^T=-I$. If we find such a $\Sigma$, then $\Tr(\Sigma)=\lim_{t\to\infty}\sum_iE[y_i(t)^2]\lim_{t\to\infty}=E[|y(t)|^2].$ If we define $\mathscr{H}=\Tr(\Sigma)$, then $H$ shows the expected distance between the opinion vector and the consensus vector at steady state. $\mathscr{H}$ is therefore a measure of the robustness of the consensus state to noise.

In this paper, we consider the possibility of an environmental signal that drives the opinions to be equal to $1$. With this modification, the dynamics can be written
\begin{equation}
\dot{x}=Lx+B(\vec{1}-x)+\xi=L_\text{f}x+B\vec{1}+\xi
\end{equation}
In this case, $\vec{1}$ becomes a globally asymptotically stable equilibrium and we can find the steady state variance around this equilibrium without rotating into the subspace orthogonal to consensus. In particular, if $C_{ij}=\lim_{t\to\infty}E[(y_i(t)-\langle y_i(t)\rangle)(y_j(t)-\langle y_j(t)\rangle)]$, then the symmetric matrix $C$ satisfies $L_\text{f}C+CL_\text{f}^T=-I$ (Claim \ref{lyapeq_derivation}).

>>>>

To rotate into the space orthogonal to the consensus vector, we can define a matrix $Q\in\R^{N-1}\times\R^N$ such that each row of $Q$ is orthogonal to $\vec{1}$ and the rows are pairwise orthogonal. Young et al. show in \cite{Young:2010fk} show that this equivalent to finding $Q$ such that $Q\vec{1}=\vec{0}$, $QQ^T=I_{N-1}$, and $Q^TQ=I_N-\frac{1}{N}\vec{1}_N\vec{1}_N^T$. If we then define $y=Qx$, $y$ is the component of $x$ orthogonal to the consensus vector. It follows that the dynamics of $y$ follow
\begin{align*}
\dot{y}&=Q\dot{x}
\\&=QLx+Q\xi
\\&=QL\big(x-\frac{1}{N}\sum_kx_k\vec{1}\big)+Q\xi \text{ since } L\vec{1}=0
\\&=QLQ^TQx+Q\xi
\\&=QLQ^Ty+Q\xi
\\&=\tilde{L}y+Q\xi.
\end{align*}
Now, $y=\vec{0}$ \emph{is} globally asymptotically stable, so analyzing its variance at steady state is a well-defined problem. Young et al. show in \cite{Young:2010fk} and we show below in Claim \ref{lyapeq_derivation} that if $\Sigma=\lim_{t\to\infty}E[y(t)y^T(t)]$, then $\Sigma$ satisfies $\tilde{L}\Sigma+\Sigma \tilde{L}^T=-QQ^T$. If we find such a $\Sigma$, then $\Tr(\Sigma)=\lim_{t\to\infty}\sum_iE[y_i(t)^2]\lim_{t\to\infty}=E[|y(t)|^2].$ If we define $\mathscr{H}=\Tr(\Sigma)$, then $H$ shows the expected distance between the opinion vector and the consensus vector at steady state. $\mathscr{H}$ is therefore a measure of the robustness of the consensus state to noise.

In this paper, we consider the possibility of an environmental signal that drives the opinions to be equal to $1$. With this modification, the dynamics can be written
\begin{equation}
\dot{x}=Lx+B(\vec{1}-x)+\xi=L_\text{f}x+B\vec{1}+\xi
\end{equation}
In this case, $\vec{1}$ becomes a globally asymptotically stable equilibrium and we can find the steady state variance around this equilibrium without rotating into the subspace orthogonal to consensus. In particular, if $C_{ij}=\lim_{t\to\infty}E[(x_i(t)-\langle x_i(t)\rangle)(x_j(t)-\langle x_j(t)\rangle)]$, then the symmetric matrix $C$ satisfies $L_\text{f}C+CL_\text{f}^T=-I$ (Claim \ref{lyapeq_derivation}).
